---
tiitle: "ENGG 6150 term Project Proposal"
author:"Jian(Kevin), Lin"
output: word_document
---



*Market Analysis*

   There are two types of turbidity meter in the market including holdheld and benchtop. According to Future Market Insight, global turbidity meter will reach one billion US dollar in 2029 end. Handhold turbidity meters will reach 400 million by 2029 end. [1]


*Current Market Competitors*
    

```{r}
brand <- c("Oakton","Hach","Extech","Thermo Scientific", "HF Scientific","Lovibond")
lowest_price <- c(1259.01, 1969.92,913.5,1804.9,1565.48,1613.36)
highest_price <- c(1617.05, 1969.92,  913.5,2224.82,1565.48,1613.36)

HandheldTurbidityMeter <-data.frame(brand,lowest_price,highest_price)

knitr::kable(HandheldTurbidityMeter,caption = "Major vendors of Handheld Turbidity Meter")

```


```{r}
Company  <- c("Protected Elsius","Genome Alberta","Xenon Pharmaceuticals Inc", "Takeda Canada Inc","BIOTECanada","MaRS Discovery District","University of Waterloo","Merck Canada","Pfizer Canada Inc","Valeant Canada","BioAuxilium Research")
Location <- c("Alberta:Calgary","Alberta:Calgary","British Columbia:Burnaby","Ontarion:Oakville","Ontario:Ottawa","Ontario:Toronto","Ontario :Waterloo","Quebec:Kirkland","Quebec:Kirkland","Quebec:Montreal","Quebec:St Laurent")
Category <- c("Industry Service & Support","Early stage biotechnology","Early stage biotechnology","Commercial biotechnolgoy","Industry Organization","Incubator & Accelerator","Research and Academia","Commercial biotechnology","Commercial biotechnology", "Industry Service & Support","Commercial biotechnology")
customers <- data.frame(Company,Location,Category)

knitr::kable(customers)
```


*Busniess Plan*

    In the first stage, a funding is required. Potential funding partner includes school enterpreship plan from guelph
university. Canadian governemnt also provides funding for enterpreship. There are many funding body in Canada govern body. 

```{r}
Organization <- c("BDC Small Business Loan","BDC Newcomer Entrepreneur","Canada Small Business Financicing Program","MaRS Investment Accelerator Fund","OCE Market Readiness Program", "OCE Voucher Programs")

Govern_body <- c("Federal","Federal","Federal","Ontario","Ontario","Ontario")

funding_body <- data.frame(funding,body)

knitr::kable(funding_body,caption = "Potential Funding bodies for Turbidity Meter Startup")

```

     Second stage is manufactuing step, we will manufacture just a few samples by myself for demo only. 

     Third stage is marketing step,I will call all of water related company to see they wants to try our new product. 

    Forth stage is to manufacture these instrument, a small lab or warewarehouse can be used to manufacture these equipement. Then send t out. 


\newpage


Alt-Reference

[1] https://www.coleparmer.ca/c/turbidity-meters. 03/05/2020.

[2] http://www.biotech.ca/biolist/. 03/05/2020. 
 
[3] https://innovation.ised-isde.canada.ca/s/group-groupe?language=en_CA&token=a0B5W000000ArMcUAK.03/05/2020

[4] https://www.mentorworks.ca/what-we-offer/government-funding/funding-regions/ontario/ . 03/05/2020





